Multi-level modelling with Openflexo/FML - A contribution to the \mpc

### 2021-05-25 8-Discussion.tex
more stuff in assessment section

  As for cross-level relationships, cross-level constraints do not have a
  specific nature. They are like any constraint a user can define on a model
  element. Therefore, if a constraint is mandatory when establishing a
  relationship between elements from different levels, the user has create it
  manually. This can be a limit of our approach: the flexibility of our tooling
  at the cost of a limited number fo automated behaviors.

@@

  In order to preserve the integrity of level contents when changes to level
  contents occur, a validation has to be triggered. The tool reports all
  inconsistencies that the user is free to fix.

@@

  Due to the nature of model federation, the models are highly reusable. Our
  solution separates the domain-specific elements from general purpose ones,
  making easily possible to apply it to other domains. 
  \noteJC{à développer + ajouter avantage de l'outil gratuit ici ?}

@@

  A strength of the approach of model federation we have adopted resides in its
  flexibility. One can extend a solution easily:

  \noteJC{comment étendre : dépend un peu des extensions, ne prendre que celle
  donnée en exemple ? ; level insertion possible : oui, vu que pas de notion de
level}

@@

>>>>

  As for cross-level relationships, cross-level constraints do not have a
  specific nature. They are like any constraint a user can define on a model
  element. Therefore, if a constraint is mandatory when establishing a
  relationship between elements from different levels, the user has to create
  it manually. This can be a limit of our approach: the flexibility of our
  tooling at the cost of a limited number of automated behaviors.

@@

  In order to preserve the integrity of level contents when changes to level
  contents occur, a validation has to be triggered. The tool reports all
  inconsistencies that the user is free to fix. Note that in our approach, the
  metamodels are built in a ad hoc way  together with the models
  (co-construction), threfore the user validates on a ad hoc basis.

@@

  Due to the nature of model federation, the models are highly reusable.
  Although we build ad hoc metamodels in our approach, our solution separates
  the domain-specific elements from general purpose ones, making easily
  possible to apply it to other domains.

@@

  A strength of the approach of model federation we have adopted resides in its
  flexibility. As we build metamodels and models together instead of fitting
  into a metamodel, our solution is more flexible. Therefore one can extend a
  solution easily. The challenge itself can be seen as a validation of the
  extensibility ability of our solution: it was decomposed into two steps
  (generic process Xsure, then ACME process) which is kind of simulation of the
  evolution of the  specification. We observed that our approach has been
  resilient to change.

  Due to the level-blind aspect of our approach, we could insert a new level,
  for instance. It would consist in creating new concepts we would link to
  other ones. Then, we would add any necessary constraints on those concepts
  and on the relashiontips linking them to the other existing concepts.

  \noteJC{comment étendre : prendre l'exemple donné ?; level insertion possible
  : oui, vu que pas de notion de level}

@@

Currently, there are no formalism to establish the semantics of the MLM
technique in our solution. \textcolor{red}{To develop…}

Our solution is fully tooled by a ``free'' ad hoc tool. We use the Openflexo
infrastructure to design models and metamodels together. In addition, our
infrastructure also produces a dedicated tool which allows processes execution.
In our approach,
